Predicting complex diseases: performance, robustness and ..utility..(impact?)

### 2017-12-04 paper/draft.tex
save

\subsection{Predictive performance measures}

@@

@@

@@

[Also return p-values?]\\

@@

\newpage
\begin{figure}[h]
\centerline{\includegraphics[width=\textwidth]{AUC}}
\caption{AUC...}\label{fig:AUC}
\end{figure}

\newpage
\begin{figure}[h]
\centerline{\includegraphics[width=\textwidth]{AUC-rel}}
\caption{Relative AUC...}\label{fig:AUC-rel}
\end{figure}

@@

\begin{figure}[h]
\centerline{\includegraphics[width=\textwidth]{ttrees}}
\caption{Results of T-Trees vs penalized logistic regression. \textbf{A.} Timing (in seconds). \textbf{B.} Number of predictors of the model. \textbf{C.} AUC. \textbf{D.} Percentage of cases in the 10\% largest scores.}\label{fig:ttrees}
\end{figure}

@@

\begin{figure}[h]
\centerline{\includegraphics[width=\textwidth]{AUC-corr}}
\caption{Percentage of cases in the 2 highest deciles of PRSs as a function of AUC.}\label{fig:AUC-corr}
\end{figure}

@@

\begin{figure}[h]
\centerline{\includegraphics[width=\textwidth]{meme}}
\caption{Meme to use on Twitter when promoting the preprint?}\label{fig:meme}
\end{figure}

>>>>

\subsection{Predictive performance measures}\label{sec:auc}

@@

\subsection{Maximum AUCs}

[MOVE IN SUPMAT AND METHODS]

Assuming that $y \sim N(0, h^2)$, we can estimate the theoretical value of the AUC that can be achieved given the heritability $h^2$ (see ..SupMat..). We report AUCs of 0.8410 and 0.9406 for respectively an heritability of 50\% and 80\%.
% wray2010genetic

@@

\subsection{Scenario \textnumero1}

In scenario \textnumero1, we compared our penalized logistic regression (``logit-simple'') with the P+T method (``PRS'') on the whole genome (Table \ref{tab:simus}). 
When there are only 30 causal SNPs, our penalized logistic regression almost reach the maximum achievable AUC (Figures \ref{fig:main-AUC-logit} \& \ref{fig:supp-AUC-logit}).
Still in terms of AUC, our penalized regression consistently performs better or equally to the ``PRS-max''. 
In the case where there are correlation between predictors (i.e.\ when we simulate 30 SNPs in the HLA region), the ``logit-simple'' method particularly performs better than the ``PRS-max'' one, with a mean AUC of 92.5\% versus 83\%, for a maximum achievable AUC of 94\% (Figure \ref{fig:main-AUC-logit}).
[NUL] Moreover, results of PRS can dramatically drop given the threshold of inclusion of SNPs in the model (Figures \ref{fig:main-AUC-PRS} \& \ref{fig:supp-AUC-PRS}).

@@

@@

\newpage
\begin{figure}[h]
\centerline{\includegraphics[width=\textwidth]{main-AUC-logit}}
\caption{Mean of AUC over 100 simulations for our penalized logistic regression (``logit-simple'') and the maximum AUC reported with the P+T method (``PRS-max''). Upper (lower) panel is presenting results for effets following a Gaussian (Laplace) distribution. Error bars are representing $\pm 2 \text{SD}$ of $10^5$ non-parametric bootstrap of the mean of AUC. The blue dotted line represents the maximum achievable AUC. [MODEL AND H2]}\label{fig:main-AUC-logit}
\end{figure}

\newpage
\begin{figure}[h]
\centerline{\includegraphics[width=\textwidth]{main-AUC-PRS}}
\caption{Mean of AUC over 100 simulations for ..the three reported PRSs... Upper (lower) panel is presenting results for effets following a Gaussian (Laplace) distribution. Error bars are representing $\pm 2 \text{SD}$ of $10^5$ non-parametric bootstrap of the mean of AUC. The blue dotted line represents the maximum achievable AUC. [MODEL AND H2]}\label{fig:main-AUC-PRS}
\end{figure}

@@

\newpage
\begin{figure}[h]
\centerline{\includegraphics[width=\textwidth]{supp-AUC-logit}}
\caption{[COPY FOR H2=0.5]}\label{fig:supp-AUC-logit}
\end{figure}

\newpage
\begin{figure}[h]
\centerline{\includegraphics[width=\textwidth]{supp-AUC-PRS}}
\caption{[COPY FOR H2=0.5]}\label{fig:supp-AUC-PRS}
\end{figure}

%\begin{figure}[h]
%\centerline{\includegraphics[width=\textwidth]{ttrees}}
%\caption{Results of T-Trees vs penalized logistic regression. \textbf{A.} Timing (in seconds). \textbf{B.} Number of predictors of the model. \textbf{C.} AUC. \textbf{D.} Percentage of cases in the 10\% largest scores.}\label{fig:ttrees}
%\end{figure}

@@

%\begin{figure}[h]
%\centerline{\includegraphics[width=\textwidth]{AUC-corr}}
%\caption{Percentage of cases in the 2 highest deciles of PRSs as a function of AUC.}\label{fig:AUC-corr}
%\end{figure}

@@
